A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2018-03-26 bioc-workflow_march2017.Rnw
Daniel's comment 1

Having added a the mouse markers to our \texttt{fData} from the
\texttt{pRolocmarkers}, we can now visualise these annotations along
the PCA plot using the \texttt{plot2D} function and then use the
\texttt{addLegend} function to map the marker classes to the
pre-defined colours. We also display the data along the first and
seventh PCs using the \texttt{dims} argument. Note that in these calls
to the \texttt{plot2D} function, we have omitted the \texttt{fcol}
argument and use of the default \texttt{"markers"} feature variable to
annotate the plot. We choose to display PCs 1 and 7 to illustrate that
while upper principal components explain much less variability in the
data (2.23\% for PC7, as opposed to 48.41\% for PC1), we see that the
mitochondrial (purple) and peroxisome (dark blue) clusters can be
differentiated, despite the apparent overlap in the visualisation of
the two first PCs (Figure \ref{fig:plotmarkers}).

>>>>

Having added a the mouse markers to our \texttt{fData} from the
\texttt{pRolocmarkers}, we can now visualise these annotations along
the PCA plot using the \texttt{plot2D} function and then use the
\texttt{addLegend} function to map the marker classes to the
pre-defined colours. \hl{As mentioned previously, PCA transforms the
original high dimensional data into a set of linearly uncorrelated
principal components such that the first accounts for as much
variability in the data as possible and each succeeding component in
turn has the highest variance possible under the constraint that it
be orthogonal to the preceding components. We saw in the previous
section how this is useful for quality control and checking
organelle seperation.  Adding marker definiton allows one to quickly
see if known residents appear in defined clusters. One must be
careful though as different organelles may be resolved in different
dimensions.} For example, we can display the data along the first and
seventh PCs using the \texttt{dims} argument. Note that in these
calls to the \texttt{plot2D} function, we have omitted the
\texttt{fcol} argument and use of the default \texttt{"markers"}
feature variable to annotate the plot. We choose to display PCs 1
and 7 to illustrate that while upper principal components explain
much less variability in the data (2.23\% for PC7, as opposed to
48.41\% for PC1), we see that the mitochondrial (purple) and
peroxisome (dark blue) clusters can be differentiated, despite the
apparent overlap in the visualisation of the two first PCs (Figure
\ref{fig:plotmarkers}).  This is further highlighted if we plot the
profiles of these two clusters using the \texttt{plotDist} function
(Fig \ref{fig:plotDist2}).
